Learning Reusable Components for Neurally--Guided Bayesian Program Learning

### 2018-05-12 nips_2018.tex
text edit examples

\begin{figure}
  \centering\begin{tabular}{ll|ll}\toprule
    Input&Output&Input&Output\\\midrule
cqbHT$>$aIKd$<$W& 	AIKD&BgZQ..PBBnD & BgZQ. \\
YBW$>$TIg$<$WS 	&TIG& qqfgg..mNIx & qqfgg. 
%DkI$>$DwKI$<$xaPoc& 	DWKI\\
%KfvTh$>$Dbl$<$OIJso 	&DBL
\\\midrule
\multicolumn{2}{l|}{$f(\text{\code{s}}) = $\code{(}$f_3$\code{ (split }\codechar{>}\code{ } }&
\multicolumn{2}{l}{$f(\text{\code{s}}) = $\code{(}$f_1$\code{ s }\codechar{.}\code{ 0)}}
\\
\multicolumn{2}{l|}{\hspace{1.1cm}\code{(upper s)) }\codechar{<}\code{)}}
\\\bottomrule
  \end{tabular}

@@

  \caption{Two string edit tasks (top) and the programs \system writes for them (bottom). $f_3$ are $f_1$  discovered DSL subroutines, defined in Tbl.~\ref{textPrimitives}.}\label{exampleTextProblem}
\end{figure}

>>>>

\begin{figure}
  \centering\begin{tabular}{ll|lll}\toprule
    Input&Output&Input 1&Input 2&Output\\\midrule
Temple Annalisa Haven 185&TAH1&Launa&Withers&Launa Withers\\
Lara Gregori Bradford&LGB& Rudolf&Akiyama&Rudolf Akiyama
%DkI$>$DwKI$<$xaPoc& 	DWKI\\
%KfvTh$>$Dbl$<$OIJso 	&DBL
\\\midrule
\multicolumn{2}{l|}{$f(\text{\code{s}}) = $\code{(}$f_2$\code{ s)}}&
\multicolumn{2}{l}{$f(\text{\code{a}},\text{\code{b}}) = $\code{(}$f_0$\code{ a (cons " " b))}}
\\
\bottomrule
  \end{tabular}

@@

  \caption{Two string edit tasks (top) and the programs \system writes for them (bottom). $f_0$ and $f_2$ are   subroutines written by \systemEnding, defined in Tbl.~\ref{textPrimitives}.}\label{exampleTextProblem}
\end{figure}
